Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Discuss ballot encryption in PV

In \term{Scantegrity}, the public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.)

In \term{Helios}, the public ballot is a hash of an encryption. \term{Helios} uses ElGamal to encrypt ballots,
which -- unlike \term{Scantegrity}'s core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, \term{Helios} uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees. \term{Scantegrity} essentially has an immensely large
key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
decrypted. \term{Helios}, however, uses known algorithms with shorter keys that could potentially be
attacked. Compromise of keys in either system would destroy their privacy guarantees.

>>>>

In \term{Scantegrity}, the public version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, keyless encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
compromise would eliminate ballot secrecy for all ballots.) But it is important to note that this
table can be reconstructed using the same pseudorandom number generator as during initial creation
along with the (shared secret) generator seed.

In \term{Helios}, the public ballot is a hash of an encryption. \term{Helios} uses ElGamal to encrypt ballots,
which -- unlike \term{Scantegrity}'s core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, \term{Helios} uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees.

With \term{\pv{}}, the submitted ballot is really just a position within a permutation of the
candidates. The \emph{position} within the permutation is not encrypted: rather, the candidate
permutation is secret and can be obtained (later in the election process) from the onion.

Considering the confirmation codes from a ballot, \term{Scantegrity} seems to have an immensely
large key that -- because it is theoretically random -- ensures that ciphertext cannot be decrypted.
But compromise of the much shorter generator seed could be used to obtain the same information.
\term{Helios} and \term{\pv{}} more simply use known algorithms with secret keys. Key compromise
would destroy the privacy guarantees of any of these systems.
